---
title: "1Phil_Shorlist"
output: html_document
---
## no sampling 
```{r}
library(stylo)
corpus_all <- load.corpus.and.parse(files = "all", corpus.dir = "Unicode_No1Phil", markup.type= "plain", corpus.lang = "Other", sampling = "no.sampling", preserve.case = FALSE, encoding = "UTF-8") 

test_corpus <- load.corpus.and.parse(files = "Demosthenes_1Phil.txt", corpus.dir = getwd(), markup.type= "plain", corpus.lang = "Other", sampling = "no.sampling", preserve.case = FALSE, encoding = "UTF-8")

corpus <- c(corpus_all, test_corpus)
corpus <- c(corpus, test_corpus)

## make frequency list
mfw <- make.frequency.list(corpus)
mfw <- mfw[1:100]
mfw <- mfw[-14] ## remove NULL value

freq <- as.data.frame.matrix(as.table(make.table.of.frequencies(corpus, mfw, absent.sensitive = FALSE)))
dim(freq)

## calculate delta
my_delta <- perform.delta(training.set = freq[1:28,], test.set = freq[29:30,], distance = "delta", no.of.candidates = 3, z.scores.both.sets = FALSE)
my_delta$ranking
```

## 1000-w samples 
```{r}
test_corpus1000 <- load.corpus.and.parse(files = "Demosthenes_1Phil.txt", corpus.dir = getwd(), markup.type= "plain", corpus.lang = "Other", sampling = "normal.sampling", sample.size = 1000, preserve.case = FALSE, encoding = "UTF-8")

corpus1000 <- c(corpus_all, test_corpus1000)
freq1000 <- as.data.frame.matrix(as.table(make.table.of.frequencies(corpus1000, mfw, absent.sensitive = FALSE)))
dim(freq1000)

my_delta1000 <- perform.delta(training.set = freq1000[1:28,], test.set = freq1000[29:31,], distance = "delta", no.of.candidates = 5, z.scores.both.sets = FALSE)
my_delta1000$ranking
my_delta1000$scores